Improving the portuguese hyphenation rules

### 2023-07-13 article/article.tex
fix #12

The original \TeX{} hyphenation algorithm was introduced by Knuth 1977
\cite{knuth1977}. It was focused on the English language and used three main
rules:(1) suffix removal; (2) prefix removal; and (3)
vowel-consonant-consonant-vowel (vccv) breaking. Tests showed it could find
40\% of the allowed hyphen locations \cite{liang1983}. The hyphenation
algorithm proposed by Frank M. Liang and adopted in \TeX{} uses the notion of
competing patterns. A database of hyphenated words is swept, looking for
hyphenating and inhibiting patterns. The algorithm introduced in \TeX{}82 uses
five alternating levels of hyphenating and inhibiting patterns. The program
for patten generation, based on a corpus, PATGEN was created Liang
\cite{liangbreitenlohner1999} and was used to create hyphenating patterns for
many languages
\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}.

>>>>

The original \TeX{} hyphenation algorithm was introduced by Knuth 1977
\cite{knuth1977}. It was focused on the English language and used three main
rules:(1) suffix removal; (2) prefix removal; and (3)
vowel-consonant-consonant-vowel (VCCV) breaking. Tests showed it could find
40\% of the allowed hyphen locations \cite{liang1983}. The hyphenation
algorithm proposed by Frank M. Liang and adopted in \TeX{} uses the notion of
competing patterns. A database of hyphenated words is swept, looking for
hyphenating and inhibiting patterns. The algorithm introduced in \TeX{}82 uses
five alternating levels of hyphenating and inhibiting patterns. The program
for patten generation, based on a corpus, PATGEN was created Liang
\cite{liangbreitenlohner1999} and was used to create hyphenating patterns for
many languages
\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}.
